---
title: "CSN Lab 4"
author: "Norbert Schlaffke & Lukas Ramroth"
date: "November 2019"
output:
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=7, fig.height=5)

library(knitr)

source('lab4.r')
```

# Introduction

hi

## Used metric

Special normalized metric by ramon...

$$
\left\langle d\right\rangle_z = \frac{\left\langle d\right\rangle - \mathbb{E}_{rla}[\left\langle d\right\rangle]}{\sigma_{rla}[\left\langle d\right\rangle]}
$$
blabla
$$
\mathbb{E}_{rla}[\left\langle d\right\rangle] = \frac{n + 1}{3}
$$
blabla
$$
\sigma_{rla}[\left\langle d\right\rangle] = \sqrt{\frac{\mathbb{V}_{r l a}[D]}{n - 1}}
$$
aaa
$$
\mathbb{V}_{r l a}[D]=\frac{n+1}{45}\left[(n-1)^{2}+\left(\frac{n}{4}-1\right) n\left\langle k^{2}\right\rangle\right]
$$

# Results

abv

```{r echo=FALSE, cache=TRUE, warning=FALSE}
kable(language_statistics,
            caption="\\label{tab:table1}Basic properties of the languages' degree sequences",
      #col.names = c("language", "N", "E", "$\\langle k \\rangle$", "$\\delta$"),
      align=c('l', 'r', 'r', 'r', 'r'))
```

```{r echo=FALSE, cache=TRUE}
plot(languages$Catalan$vertices, languages$Catalan$mean_length_normalized, xlab = "vertices", ylab = "mean dependency length")
plot(languages_aggr$Catalan$vertices, languages_aggr$Catalan$mean_length_normalized, xlab = "vertices", ylab = "mean dependency length")
```

```{r echo=FALSE, cache=TRUE}
print_est("Catalan")
```

# Discussion

jh

# Methods

no loglog space since negative values, so guessing starting parameters by hand.
Also Func1 makes no sense, since it cant by negative...

used metrics

* $f(n)=a n^{b}$ (model 2), a power-law model
* $f(n)=a n^{b}+d$ (model 2+), a power-law model with residual
* $f(n)=a e^{c n}$ (model 3), an exponantial model
* $f(n)=a \log n$ (model 4), a logarithmic model
